Deciding Bitvector Termination with Program Synthesis

### 2014-07-04 papers/termination/paper.tex
PSPACE complete

>>>>

Since termination for bitvector programs is known to be PSPACE-complete~\cite{DBLP:conf/tacas/CookKRW10} it
is perhaps unsurprising that we are able to decide it.  We will now show that our time complexity is
asymptotically a function of the Kolmogorov complexity of the (non-)termination proof, and argue heuristically
that this gives our procedure various desirable qualities.
